Model Finding for Recursive Functions in SMT\thanks{ This research is partially supported by the Inria technological development action ``Contre-exemples Utilisables par Isabelle et Coq'' (CUIC). }

### 2015-05-06 tex/main.tex
tuned

\begin{definition}%
\rm
A formula $\varphi$ is in \emph{definitional form with respect to} $n$ distinct function symbols
$\{ \con{f}_1, \ldots, \con{f}_n \} \subseteq \sfuns{\Sigma}$ if it is of the form
%
%\kern-\abovedisplayskip
%\kern+\abovedisplayshortskip
%
\begin{equation} \label{eq:wdf}
(\forallf{\con{f}_1} \vec x_1.\; \varphi_1) \wedge \cdots \wedge
(\forallf{\con{f}_n} \vec x_n.\; \varphi_n) \wedge \psi
\end{equation}
%
where $\psi$ contains no function definitions.
We call $\psi$ the \emph{conjecture} of $\varphi$.
%\ct{Don't we need additional restrictions on the $\varphi_i$'s here?
%(E.g., they are quantifier-free, or perhaps existential or containing only let binders.)}
% Now fixed above -ajr
\end{definition}

@@

\begin{definition}
Given a set of function definitions $\DDD = \{ \forallf{f_1} \vec x.\;
\varphi_1, \ldots, \forallf{f_n} \vec x.\; \varphi_n \}$, a formula $\varphi$
is \emph{closed under function expansion with respect to $\DDD$} if
\begin{eqnarray}
\varphi \models_T \bigwedge_{i=1}^n \{ \varphi_i[ \vec t / \vec x ] \mid f_i( \vec t ) \in \terms( \varphi ) \}
\end{eqnarray}
The set $\DDD$ is \emph{admissible} if whenever there exists a model for $\varphi$ that is closed under function expansion,
there exists a model for $\varphi \wedge \forallf{f_1} \vec x.\; \varphi_1 \wedge \cdots \wedge \forallf{f_n} \vec x.\; \varphi_n$.
\end{definition}

>>>>

\begin{definition}\rm
A formula $\varphi$ is in \emph{definitional form with respect to} $n$ distinct function symbols
$\{ \con{f}_1, \ldots, \con{f}_n \} \subseteq \sfuns{\Sigma}$ if it is of the form
%
%\kern-\abovedisplayskip
%\kern+\abovedisplayshortskip
%
\begin{equation} \label{eq:wdf}
(\forallf{\con{f}_1} \vec x_1.\; \varphi_1) \wedge \cdots \wedge
(\forallf{\con{f}_n} \vec x_n.\; \varphi_n) \wedge \psi
\end{equation}
%
where $\psi$ contains no function definitions.
We call $\psi$ the \emph{conjecture} of $\varphi$.
%\ct{Don't we need additional restrictions on the $\varphi_i$'s here?
%(E.g., they are quantifier-free, or perhaps existential or containing only let binders.)}
% Now fixed above -ajr
\end{definition}

@@

\begin{definition}\rm
Given a set of function definitions $\DDD = \{ \forallf{f_1} \vec x.\;
\varphi_1, \ldots, \forallf{f_n} \vec x.\; \varphi_n \}$, a formula $\varphi$
is \emph{closed under function expansion with respect to $\DDD$} if
\[\varphi \models_T \bigwedge_{i=1}^n \{ \varphi_i[ \vec t / \vec x ] \mid f_i( \vec t ) \in \terms( \varphi ) \}\]
The set $\DDD$ is \emph{admissible} if whenever there exists a model for $\varphi$ that is closed under function expansion,
there exists a model for $\varphi \wedge \forallf{f_1} \vec x.\; \varphi_1 \wedge \cdots \wedge \forallf{f_n} \vec x.\; \varphi_n$.
\end{definition}
